---
title: "Hiking Dashboard – GPX Summary"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
```

## Overview

This report summarizes hiking and walking routes exported from Strava as GPX files.
It provides an interactive map of all trails and a simple statistical overview.

---

## Load data

```{r load-data}
library(sf)
library(leaflet)
library(stringr)
library(dplyr)

DATA_DIR <- "data"

gpx_files <- list.files(DATA_DIR, pattern = "\\.gpx$", full.names = TRUE)
stopifnot(length(gpx_files) > 0)

traces <- lapply(gpx_files, function(f) {
  st_read(f, layer = "tracks", quiet = TRUE) |>
    mutate(
      randonnee = str_remove(basename(f), "\\s*\\(\\d+\\)\\.gpx$") |>
                  str_remove("\\.gpx$")
    )
})

traces_sf <- do.call(rbind, traces)

# Distance in kilometers
traces_sf$distance_km <- as.numeric(st_length(traces_sf)) / 1000
```

---

## Trail map

```{r map}
leaflet() |>
  addTiles() |>
  addPolylines(
    data = traces_sf,
    color = "#08306B",
    weight = 6,
    opacity = 0.3,
    popup = ~paste0(
      "<b>", randonnee, "</b><br>",
      "Distance: ", round(distance_km, 2), " km"
    )
  )
```

---

## Summary table

```{r summary}
summary_df <- traces_sf |>
  st_drop_geometry() |>
  group_by(randonnee) |>
  summarise(
    passages = n(),
    total_distance_km = round(sum(distance_km), 2),
    average_distance_km = round(mean(distance_km), 2)
  ) |>
  arrange(desc(passages), desc(total_distance_km))

summary_df
```

---

## Notes

- Trail frequency is inferred visually through line overlap on the map.
- Only GPX track geometry is used.
- No personal or physiological data is processed.

This document is intended as a lightweight, reproducible hiking activity summary.
